Challenges and Solutions of Developing and Implementing a Novel Desktop-as-a-Service

### 2024-05-03 paper.tex
Some language improvements

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning, shapes.geometric}
\usepackage{adjustbox}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
	Implementing a Novel Desktop-as-a-Service}
%
\titlerunning{Challenges and Solutions of Developing and
	Implementing a Novel DaaS}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun \and
	Johannes Bouché}
% \author{Christian Baun\orcidID{0009-0004-9955-3752} \and
% 	Johannes Bouché\orcidID{TODO}}
%
\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering,\\
	Frankfurt University of Applied Sciences,\\
	Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
	\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
	Desktop-as-a-Service (DaaS) is a cloud service category with a tremendous potential for improving the everyday work of running and using applications. However, existing DaaS solutions have several drawbacks, which have limited the popularity of this service category in the past. Our novel DaaS solution called DESIGN not only overcomes the limitations of existing solutions but also offers significant benefits. It has the potential to revolutionize the way we use applications, supporting non-modified Linux and Windows applications with just a browser on the client side. This paper describes some of the knowledge we gained during the development because of the challenges we faced and the solutions we found.

@@

This paper discusses challenges during the development and implementation of a novel Desktop-as-a-Service (DaaS) solution called DESIGN that enables the deployment and usage of unmodified Linux and Windows applications in the same way as web applications and can run inside public resources but can also be deployed in a private context. Since all interaction with DESIGN and the applications that reside inside is done via a user's web browser, the users can use any client, no matter what hardware or host operating system it is compromised of. A browser is the only software component required to use the novel DaaS service.

Undoubtedly, the development of a feature-rich DaaS system is a complex task, riddled with numerous obstacles and challenges. This paper meticulously addresses these challenges, categorizing them under compatibility, performance, stability, and usability. It not only brings these obstacles to light but also presents the solutions we devised to overcome them, along with the valuable lessons we learned in the process.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{positioning, shapes.geometric}
\usepackage{adjustbox}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
	Implementing a Novel Desktop-as-a-Service}
%
\titlerunning{Challenges and Solutions of Developing and
	Implementing a Novel DaaS}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun \and
	Johannes Bouché}
% \author{Christian Baun\orcidID{0009-0004-9955-3752} \and
% 	Johannes Bouché\orcidID{TODO}}
%
\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering,\\
	Frankfurt University of Applied Sciences,\\
	Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
	\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Desktop-as-a-Service (DaaS) is a cloud service category with tremendous potential for improving the everyday work of running and using applications. However, existing DaaS solutions have several drawbacks, which have limited the popularity of this service category in the past. Our novel DaaS solution, DESIGN, overcomes existing solutions' limitations and offers significant benefits. It can potentially revolutionize how we use applications, supporting non-modified Linux and Windows applications with just a browser on the client side. This paper describes some of the knowledge we gained during the development because of the challenges we faced and the solutions we found.

@@

This paper discusses challenges during the development and implementation of a novel Desktop-as-a-Service (DaaS) solution called DESIGN that enables the deployment and usage of unmodified Linux and Windows applications in the same way as web applications and can run inside public resources but can also be deployed in a private context. Since all interaction with DESIGN and the applications inside is done via a user's web browser, the users can use any client, no matter what hardware or host operating system it is compromised of. A browser is the only software component required to use the novel DaaS service.

Undoubtedly, developing a feature-rich DaaS system is a complex task, riddled with numerous obstacles and challenges. This paper meticulously categorizes these challenges into compatibility, performance, stability, and usability. It brings these obstacles to light and presents the solutions we devised to overcome them, along with the valuable lessons we learned in the process.
